R Notebook

### 2022-04-01 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

# Read in the relevant data
CPDMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
                                hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
                                hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed"))

sixFourMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed"))

CPDMismatchData = lapply(CPDMismatchDataFilePaths, fread)
sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, fread)

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) simplifyTable(filterResults(x)))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) simplifyTable(filterResults(x)))

@@

plotMismatchTypeFrequencies(CPDMismatchData$hr1, title = "CPD 1hr Mismatch Type Frequency")
plotMismatchTypeFrequencies(CPDMismatchData$hr24, title = "CPD 24hr Mismatch Type Frequency")
plotMismatchTypeFrequencies(CPDMismatchData$hr48, title = "CPD 48hr Mismatch Type Frequency")

plotMismatchTypeFrequencies(sixFourMismatchData$hr1, title = "6-4 1hr Mismatch Type Frequency")

@@

plotMismatchPositionFrequencies(CPDMismatchData$hr1, includedTypes = c("C>T"), 
                                title = "CPD 1hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "CPD 1hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(CPDMismatchData$hr24, includedTypes = c("C>T"), 
                                title = "CPD 24hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "CPD 24hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(CPDMismatchData$hr48, includedTypes = c("C>T"), 
                                title = "CPD 48hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr48, omittedTypes = c("C>T"), 
                                title = "CPD 48hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(sixFourMismatchData$hr1, includedTypes = c("C>T"), 
                                title = "6-4 1hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(sixFourMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "6-4 1hr !C>T Mismatch Positions")

>>>>

# Read in the relevant data
CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
CPDMismatchDataFilePaths$rep1 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed")
)
CPDMismatchDataFilePaths$rep2 = list(
  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches.bed"),
  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches.bed"),
  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches.bed"),
  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches.bed")
)

sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
sixFourMismatchDataFilePaths$rep1 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed")
)
sixFourMismatchDataFilePaths$rep2 = list(
  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches.bed"),
  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches.bed"),
  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches.bed")
)

CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
))

@@

for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste("CPD", names(CPDMismatchData)[i], 
                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste("6-4", names(sixFourMismatchData)[i], 
                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}

@@

for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
